DynaProg for Scala

### 2013-01-25 docs/report/benchmarks.tex
Final report.

\subsection{Smith-Waterman (affine gap cost)}
% CPU: DynaProg(Scala), hand optimized C, GAPC and ADPFusion
% GPU: DynaProg(CUDA), hand optimized CUDA, CUDAlign
Smith-Waterman with affine gap cost is a serial problem, which is not directly the focus of our project but nevertheless can be addressed efficiently. The problem formal description (\S\ref{swat_affine}) uses 3 matrices. However, since two of these matrices only propagate information along line or column, it is possible to encode this information in a wavefront (see \S\ref{calc_simplifications}) instead of maintaining it in a memory-expensive matrix. This knowledge is leveraged by \cite{ATLP}, however, in our case, we cannot describe the wavefront in the grammar and need to maintain explicitly 3 matrices, thereby multiplying by 3 the memory usage\footnote{Actually slightly less than 3 because we replace 2 matrices in $O(n^2)$ by two vectors in $O(n)$}.

>>>>

\subsection{Smith-Waterman (affine gap cost)}
% CPU: DynaProg(Scala), hand optimized C, GAPC and ADPFusion
% GPU: DynaProg(CUDA), hand optimized CUDA, CUDAlign
Smith-Waterman with affine gap cost is a serial problem, which is not directly the focus of our project but nevertheless can be addressed efficiently. The problem formal description (\S\ref{swat_affine}) uses 3 matrices. However, since two of these matrices only propagate information along line or column, it is possible to encode this information in a wavefront (see \S\ref{calc_simplifications}) instead of maintaining it in a memory-expensive matrix. This knowledge is leveraged by \cite{gpu_atlp}, however, in our case, we cannot describe the wavefront in the grammar and need to maintain explicitly 3 matrices, thereby multiplying by 3 the memory usage\footnote{Actually slightly less than 3 because we replace 2 matrices in $O(n^2)$ by two vectors in $O(n)$}.
